LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-10-03 main.tex
Add FIXME comments to indicate potential problems & needed revisions

\documentclass{elsarticle}

\usepackage{amsmath}
\usepackage{commath}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage[numbered,framed]{mcode}
\usepackage{cleveref}

@@

\author{G.~Haller\corref{cor}}
\ead{georgehaller@ethz.ch}

@@

\begin{keyword}
Dynamical systems \sep Lagrangian coherent structures \sep Invariant manifolds \sep Mixing \ Mathematical software

@@

The data is given at a spatial resolution of $1/4°$ and a temporal resolution of $7\,\mathrm{days}$. Due to the discrete data, defining the right hand side of \cref{eq:dtlon} and \cref{eq:dtlat} involves spline interpolation in space and time. An interpolant is generated first, then the function \lstinline!flowdata_derivative! evaluates the interpolants for the zonal and meridional velocity at the needed coordinates. \Cref{l:griddedInterp} shows the relevant part of the code in LCS Tool's ocean demo file \lstinline!hyperbolic_shear_lcs.m!. In \crefrange{ll:interpolation start}{ll:interpolation end}, the commands for the interpolation are given of the velocity dataset are given.

@@

% Local Variables:
% ispell-dictionary: "en_US"
% End:
% LocalWords:  stretchline stretchlines incompressible gyre eigenvector eigenvectors incompressibility dataset datasets LCS LCSs Lyapunov Bickley Rossby timespan variational adaptively vortices parametrise advected strainlines minima extremal FTLE MATLAB maxima geostrophic shrinkline shrinklines

>>>>

% FIXME Add 5p option to get JCompSci two column layout
\documentclass{elsarticle}

\usepackage{amsmath}
\usepackage{commath}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage[numbered,framed]{mcode}
\usepackage{cleveref}

@@

% FIXME Confirm George can be corresponding author
\author{G.~Haller}
\ead{georgehaller@ethz.ch}

@@

\begin{keyword}
% FIXME Match keywords and PACS and MSC classifications
% FIXME Consult previous publications to find keywords
Lagrangian coherent structures \sep Mathematical software \sep Dynamical systems \sep Invariant manifolds \sep Mixing

@@

The data is given at a spatial resolution of $1/4\degree$ and a temporal resolution of $7\,\mathrm{days}$. Due to the discrete data, defining the right hand side of \cref{eq:dtlon} and \cref{eq:dtlat} involves spline interpolation in space and time. An interpolant is generated first, then the function \lstinline!flowdata_derivative! evaluates the interpolants for the zonal and meridional velocity at the needed coordinates. \Cref{l:griddedInterp} shows the relevant part of the code in LCS Tool's ocean demo file \lstinline!hyperbolic_shear_lcs.m!. In \crefrange{ll:interpolation start}{ll:interpolation end}, the commands for the interpolation are given of the velocity dataset are given.

@@

% FIXME Keywords are required to be in British English (http://www.elsevier.com/journals/journal-of-computational-science/1877-7503/guide-for-authors), so should switch entire document to British English
% Local Variables:
% ispell-dictionary: "en_US"
% End:
% LocalWords:  stretchline stretchlines incompressible gyre eigenvector eigenvectors incompressibility dataset datasets LCS LCSs Lyapunov Bickley Rossby timespan variational adaptively vortices parametrise advected strainlines minima extremal FTLE MATLAB maxima geostrophic shrinkline shrinklines
